Improving the Fidelity of Redox Flow Battery Schedule Optimisation for more Accurate Techno-economic Analyses.

### 2018-11-21 Paper/main.tex
Update main.tex

\begin{abstract}
Redox Flow Battery (RFB) systems are promising technologies for the multi-hour electrical energy storage that would be necessary in a future low carbon emission  electrical grids based on wind and solar power. In order to perform techno-economic analyses (TEA) on these systems it is necessary to calculate potential revenue for realistic applications, ideally under optimal operation (scheduling). In this work a novel schedule optimisation framework is introduced in which coulombic and voltaic components are separated, and the problem variablised in terms of current-density rather than power. This framework allows the expression of ohmic losses as a convex quadratic function of current-density in the objective function while maintaining all linear constraints. It is demonstrated for an arbitrage application involving a vanadium RFB that the consideration of variable voltaic losses results in a significant improvement to the accuracy of revenue estimation when compared to the typical linear programming (LP) approach where a fixed efficiency is assumed. The quadratic formulation is more readily solvable than alternative approaches reported in the literature, with minimal increase to solve time compared to the LP approach. The fidelity of the RFB representation is further increased by expressing open cell voltage as a function of state of charge (SOC). At low SOC, the current-density required for a given power is greater, and hence the ohmic losses are higher. In a third development, a linear constraint is applied to the working cell-voltage, resulting in current-density restriction at high SOC in order to avoid hydrogen and oxygen evolution. This feature would also be useful for schedule optimisation of Li-ion batteries, where voltage is an important consideration. The introduced framework may be further employed to assist in the optimal design of future RFB systems for specific applications.

@@

\begin{itemize}
    \item Quadratic expression of $I^2R$ ohmic losses in the objective function under linear constraints.
    \item Open cell voltage (OCV) as a function of SOC
    \item Maximum cell voltage constraint in terms of OCV and overpotential
\end{itemize}

>>>>

\begin{abstract}
Redox Flow Battery (RFB) systems are promising technologies for the multi-hour electrical energy storage that would be necessary in a future low carbon emission  electrical grids based on wind and solar power. In order to perform techno-economic analyses (TEA) on these systems it is necessary to calculate potential revenue for realistic applications, ideally under optimal operation (scheduling). In this work a novel schedule optimisation framework is introduced in which coulombic and voltaic components are separated, and the problem variablised in terms of current-density rather than power. This framework allows the expression of ohmic losses as a convex quadratic function of current-density in the objective function while maintaining all linear constraints (NLP). It is demonstrated for an arbitrage application involving a vanadium RFB that the consideration of variable voltaic losses results in a significant improvement to the accuracy of revenue estimation when compared to the typical linear programming (LP) approach where a fixed efficiency is assumed. The introduced NLP formulation is more readily computable than alternative approaches reported in the literature, with minimal increase to solve time compared to the LP approach. The fidelity of the RFB representation is further increased by expressing open cell voltage as a function of state of charge (SOC). At low SOC, the current-density required for a given power is greater, and hence the ohmic losses are higher. In a third development, a linear constraint is applied to the working cell-voltage, resulting in current-density restriction at high SOC in order to avoid hydrogen and oxygen evolution. This feature would also be useful for schedule optimisation of Li-ion batteries, where voltage is an important consideration. The introduced framework may be further employed to assist in the optimal design of future RFB systems for specific applications.

@@

\begin{itemize}
    \item Quadratic expression of ohmic losses ($I^2R$) in the objective function under linear constraints.
    \item Open cell voltage (OCV) as a function of SOC
    \item Maximum cell voltage constraint in terms of OCV and overpotential
\end{itemize}
